msc dissertation

### 2021-07-14 msc dissertation code.Rmd
data

---
title: "msc dissertation"
author: "Halleyson Li"
date: "14/07/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

This is an R Markdown document. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

>>>>

---
title: "msc dissertation"
author: "Halleyson Li"
date: "'r Sys.Date()'"
output: html_document
line-citations: apalike
linkcolor: blue
frontsize: 12pt
---

\newpage

# *Notes*{-}
1. The GitHub repository for this project could access through [here](https://github.com/halleyson/msc-dissertation.git)

# Loading data

```{r, message=FALSE}

library(readr)

pennycook1 <- read_csv("Pennycook et al._Study 1.csv")
Pennycook2 <- read_csv("Pennycook et al._Study 2.csv")

```
